---
title: "Activity"
author: "Marius Nicolescu"
date: "7 noiembrie 2015"
output: html_document
---


## Loading and preprocessing the data, examanition data

```{r, echo=TRUE}
library(lubridate)
library(stringr)
setwd("~/R/Reproducible Research")
activity<-read.csv("activity.csv", sep=",")
summary(activity)
#single days 
date<-unique(activity$date)
#
i<-rep(0,length(date))
stepsdays<-rep(0,length(date))
#total steps per day
for(i in 1:length(date)){stepsdays[i]<-sum(activity[activity$date==date[i],]$steps,na.rm = TRUE)}

```

##Calculate the total number of steps taken per day

```{r}
i<-rep(0,length(date))
stepsdays<-rep(0,length(date))
#total steps per day
for(i in 1:length(date)){stepsdays[i]<-sum(activity[activity$date==date[i],]$steps,na.rm = TRUE)}

```


##Mean and  median of steps of days

```{r}
mean(stepsdays)

median(stepsdays)
```

##Histogram  of the total number of steps taken each day 


```{r, echo=FALSE}
hist(stepsdays,n=20)
```

## Average daily activity pattern
```{r}
time<-(strptime(str_pad(as.character(activity[,3]),4,side="left",pad="0"),"%H%M"))
#dattee days in activity as format time 
dattee<-strptime(as.character.Date(activity[,2]),"%Y-%m-%d")
year(time)<-year(dattee)
day(time)<-day(dattee)
month(time)<-month(dattee)

plot(time,activity$steps,type = "l")

datte<-strptime(as.character.Date(date),"%Y-%m-%d")
plot(datte,stepsdays,type="l")
```

##Average daily activity pattern

```{r}
# average number of steps taken, averaged across all days 
interval<-unique(activity$interval)
 j<-0
 intervalmean<-rep(0,length(interval))
for( j in 1:length(interval)){intervalmean[j]<-mean(activity[activity$interval==interval[j],]$steps,na.rm=TRUE)}
#plot average 
plot(intervalmean,type="l", col="red")


```

#Maximum step
```{r}
max(intervalmean)

```

#Number of Na.s

```{r}
length(activity[is.na(activity$steps)==TRUE,]$steps)
activity1<-activity
```

##Imputing missing values
```{r}
interval<-unique(activity$interval)
activity1<-activity

intervalmean<-as.data.frame(cbind(intervalmean,interval))
for(i in 1:length(activity1$steps))
    {if(is.na(activity1$steps[i]))
    {
          activity1$steps[i]<-intervalmean[intervalmean$interval==activity1$interval[i],]$intervalmean} 
      }
stepsdays1<-rep(0,length((date)))
for(i in 1:length(date)){stepsdays1[i]<-sum(activity1[activity1$date==date[i],]$steps)}


```

##Mean, median hitogram of steps of days whitout missing
```{r}
mean(stepsdays1)
median((stepsdays1))
hist(stepsdays1,n=20)
plot(datte,stepsdays1,type="l")

```



##Weekday Weekend

```{r}
wdat<-weekdays(datte)
wend<-as.factor(!(weekdays(datte) %in% c('duminicã','sâmbãtã')))

par(mfrow=c(1,2),mar=c(4,4,2,1))
plot(datte[wend==TRUE],stepsdays[wend==TRUE],col="red")
plot(datte[wend==FALSE],stepsdays[wend==FALSE],col="blue")




```

